{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-21 draft.tex
Revised the introduction and added more reference.

\begin{itemize}
\item Need lots of manually labelled examples.
\item Too expensive to deploy a DNN, even a trained one, due to its
  power consumption. Do we have a reference on this?
\end{itemize}

>>>>

The recent progress on development of convolutional neural networks
(CNN) is astonishing as since the AlexNet \cite{krizhevsky12} broke
the record for the ImageNet competition, at every year, new and better
results are reported. Moreover, there have been many attempts to
deploy CNN on the mobile devices
\cite{wu2016quantized,giusti2015}. But the inherent limitation of such
a supervised learning based object tracking is that an either online
\cite{nam2016} or offline \cite{held2016} training tracker has to be
prior to deploy the algorithm.
